\documentclass{propositions}

%% Turn off page numbering for the propositions and make the margins on both
%% sides equal and symmetrical.
\geometry{twoside=false}
\pagestyle{empty}

\RequirePackage{unicode-math}
\usepackage{setspace}

\setmainfont[Path = fonts/libertinus/, ItalicFont=libertinusserif-italic.otf, BoldFont=libertinusserif-bold.otf, BoldItalicFont=libertinusserif-bolditalic.otf]{libertinusserif-regular.otf}
\setsansfont[Path = fonts/libertinus/, BoldFont=libertinussans-bold.otf, ItalicFont=libertinussans-italic.otf]{libertinussans-regular.otf}
\setmathfont[Path = fonts/libertinus/]{libertinusmath-regular.otf}
\setmonofont[Scale=MatchLowercase, Path=fonts/inconsolata/]{Inconsolata-Regular.ttf}
%% The default style for text is Tahoma (sans-serif).
%\renewcommand*\familydefault{\rmfamily}

\begin{document}

%% Specify the title and author of the thesis. This information will be used on
%% both the English and Dutch side and in the metadata of the final PDF.
\title{Decentralization and Disintermediation\\ in Blockchain-based Marketplaces}
\author{Marinus Abraham}{de Vos}

\begin{center}

{\Large\titlefont\bfseries Propositions}

\medskip

accompanying the dissertation

\medskip

%% Print the title.
\begin{spacing}{1.15}
{\makeatletter
\titlestyle\bfseries\large\@title
\makeatother}
\end{spacing}

%% Print the optional subtitle.
{\makeatletter
\ifx\@subtitle\undefined\else
    \titlefont\titleshape\@subtitle
\fi
\makeatother}

\medskip

by

\medskip

%% Print the full name of the author.
\makeatletter
{\large\titlefont\bfseries\@firstname\ {\titleshape\@lastname}}
\makeatother

\end{center}

\bigskip

\begin{enumerate}
	
\item Pair-wise accounting is an effective approach to decentralize and disintermediate the fundamental aspects of blockchain-based marketplaces. \emph{[This thesis]}

\item The detection of counterparty fraud in combination with community exclusion is a viable strategy to facilitate low-risk exchange of assets between traders without central authority or trusted intermediaries. \emph{[This thesis]}

\item Decentralized matchmaking in peer-to-peer markets can be achieved with both efficiency and fairness guarantees. \emph{[This thesis]}

\item Trying to eliminate all risks in electronic marketplaces is futile and counterproductive.

\item Atomic swaps are far from atomic.

\item Smart contracts are the Achilles heel of any blockchain system and are likely to lead to the downfall of Decentralized Finance (DeFi).

\item Complicated ideas cannot result in practical decentralized systems.

\item Any decentralized system is prone to centralization.

\item Implementing a distributed algorithm is an undervalued but excellent approach to thoroughly understand its working and limitations.

\item Unambiguous government communication is a crucial requirement to reduce the spread of the COVID-19 virus.

\end{enumerate}

\bigskip
\bigskip

%% Apart from the name and title of the supervisor, the following text is
%% dictated by the promotieregelement.
\begin{center}
These propositions are regarded as opposable and defendable, and have been approved as such by the
promotors Prof.\ dr.\ D.H.J. Epema and Dr.\ ir.\ J.A.\ Pouwelse.
\end{center}

%% \clearpage
%% {\selectlanguage{dutch}

%% \begin{center}

%% {\Large\titlefont\bfseries Stellingen}

%% \bigskip

%% behorende bij het proefschrift

%% \bigskip

%% %% Print the title.
%% {\makeatletter
%% \titlestyle\bfseries\large\@title
%% \makeatother}

%% %% Print the optional subtitle.
%% {\makeatletter
%% \ifx\@subtitle\undefined\else
%%     \titlefont\titleshape\@subtitle
%% \fi
%% \makeatother}

%% \bigskip

%% door

%% \bigskip

%% %% Print the full name of the author.
%% \makeatletter
%% {\large\titlefont\bfseries\@firstname\ {\titleshape\@lastname}}
%% \makeatother

%% \end{center}

%% \bigskip
%% \bigskip

%% \begin{enumerate}

%% \item Stelling 1.
%% \item Stelling 2.
%% \item Stelling 3.
%% \item Stelling 4.
%% \item Stelling 5.
%% \item Stelling 6.
%% \item Stelling 7.
%% \item Stelling 8.
%% \item Stelling 9.
%% \item Stelling 10.

%% \end{enumerate}

%% \bigskip
%% \bigskip

%% %% Apart from the name and title of the supervisor, the following text is
%% %% dictated by the promotieregelement.
%% \begin{center}
%% Deze stellingen worden opponeerbaar en verdedigbaar geacht en zijn als zodanig goedgekeurd door de promotoren prof.\ dr.\ A.\ van Deursen and dr.\ A.\ Zaidman.
%% \end{center}

%% }

\end{document}

