\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\setheader{Acknowledgments}

While it is often said that pursuing a PhD can be a solitary and tough process, I enjoyed most aspects of it.
However, I would not have completed this journey were it not for the continuous support by colleagues, friends, and family!

First, I would like to thank Johan Pouwelse, my promotor and daily supervisor.
Under your supervision, there has not been a single day when I ran out of ideas or was unmotivated to continue, even after yet another paper rejection.
Our random and unorganized discussions, whether or not with other lab members, have been a great source of inspiration.
Your leadership and advice have tremendously helped me to become an independent researcher and to get my ideas published in the scientific community, which was definitely not always easy.
I highly value your relentless focus on practicality and usability (\enquote{no passing grade without running code}).
Also, I am grateful for the opportunities you gave me to (co-)supervise BSc and MSc students, which is an activity I very much enjoy.

I would also like to express my gratitude to my promotor Dick Epema, who was always willing to bring my research work to the next level by identifying both fundamental flaws and minor presentation issues.
Your knowledge, together with your thorough and critical feedback, has helped me to improve my writing skills, research papers and this thesis.
This feedback has also been instrumental in getting various papers published.

I thank all my colleagues for making the office life very enjoyable.
Quinten, Egbert, and Sandip: I fondly remember the times we worked on Tribler and the conversations we had in our old office, most of the time around the coffee machine (drinking coffee made up quite a part of my PhD life\emojicoffee{}).
Bulat, thank you for the many in-depth discussions we had about our research, science, and many other topics.
These conversations have definitely influenced some of the ideas in this thesis. Also, they have motivated me to be more critical of my own research (and of the research of others!).
Can, Georgy and Mitchell, thank you for your help as co-author on various papers!
I additionally thank Georgy for providing new insights from a socio-technological perspective on the work we produce as a lab, which also helped me to think about the implications of my research beyond distributed systems.
Ayman, thank you for inviting me to work together on an energy trading platform; I have learned many new things about your field!
I would also like to thank Elric, Vadim, Alexander and Andrew for our fruitful collaborations on Tribler.
Tamara, Kim, and Sophie: thank you for taking care of our administrative burdens!
I also would like to thank the graduate school for organizing a physical defence ceremony, despite the ongoing COVID-19 pandemic.

Besides the people directly involved in my research, I extend my gratitude to a large and dynamic group of people with whom I spent many Wednesday evenings playing games, eating pizza and/or drinking beer in the /pub and the Doerak Café.
These evenings were very helpful in unwinding from the (sometimes hectic) academic life.
Otto, as the regular member of this group, thank you for the many conversions and coffee/beer talks that we had!
I also thank you for your technical support when we had issues with our Tribler infrastructure.
I would also like to thank Stefan, Jesse, Hans, Ernst, Niels, Maria, Thomas, Liam, Gijs, Tim, Chris, Jetse, Alexander, Sacheendra, Taraneh, and others who occasionally joined for the Wednesday evening activities (there are just too many to list here!).

I am grateful for the many memories I made with friends.
Laurens, thank you for the many projects we worked on, the games we played, the movies and tv shows we watched (most of which seem to be cancelled for some reason), and in general, for great memories since we both started our BSc in Delft!
Laurens, Anton and Martijn: thank you for the many trips during the summer and winter holidays that we made within and outside Europe, and whether or not accompanied by others.
I will never forget that feeling after we (finally) reached the summit of Mount Fuji (and the realisation that we still had to go all the way down...)!\emojifuji{}

Last but definitely not least, I would like to thank my parents for their continuous support.
I would also like to thank Walter for teaching me many new skills during the construction of our \enquote{emergency} apartment.

\begin{flushright}
{\makeatletter\itshape
    Martijn
\makeatother}
\end{flushright}
