\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}
\setheader{List of Publications}
\label{publications}

%% We use the 'etaremune' environment (the reverse of 'enumerate') to get a
%% numbered list of publications in reverse chronological order. If the list of
%% authors is long, it might be useful to emphasize your own name with \textbf.
\begin{etaremune}{%\small
		
\item[1.] \textbf{Martijn de Vos}, Georgy Ishmaev and Johan Pouwelse, Decentralizing Components of Electronic Markets to Prevent Gatekeeping and Manipulation\\
\emph{Under review.}
		
\item[2.] Bulat Nasrulin, \textbf{Martijn de Vos} and Johan Pouwelse, Revealing the Limitations of Blockchain Performance Through Transaction Benchmarking\\
\emph{Under review.}

%\item[2.] Jan Rellermeyer, \textbf{Martijn de Vos}, Quinten Stokkink, Can Umut  and Johan Pouwelse, The Future of Blockchain Is Not (Just) a Chain\\
%\emph{Under review.}

\item[\faFileTextO~~3.] \textbf{Martijn de Vos} and Johan Pouwelse, ConTrib: Maintaining Fairness in Decentralized Big Tech Alternatives by Accounting Work\\
\emph{Under review.}

\item[\faFileTextO~~4.] \textbf{Martijn de Vos} and Johan Pouwelse, ConTrib: Universal and Decentralized Accounting in Shared-Resource Systems\\
In \emph{Proceedings of the 1st International Workshop on Distributed Infrastructure for Common Good (DICG'20)}, Delft, The Netherlands, 2020.

\item[5.] Ayman Esmat, \textbf{Martijn de Vos}, Yashar Ghiassi-Farrokhfal, Peter Palensky, Dick Epema, A Novel Decentralized Platform for Peer-to-Peer Energy Trading Market with Blockchain Technology\\
In \emph{Applied Energy}, 2020, Elsevier.

\item[\faFileTextO~~6.] \textbf{Martijn de Vos}, Georgy Ishmaev, and Johan Pouwelse, MATCH: A Decentralized Middleware for Fair Matchmaking In
Peer-to-Peer Markets\\
In \emph{Proceedings of the 20th International Middleware Conference (Middleware'20)}, Delft, The Netherlands, 2020. Acceptance Rate 25\% (30/119)

\item[\faFileTextO~~7.] \textbf{Martijn de Vos}, Can Umut Ileri and Johan Pouwelse, XChange: A Universal Mechanism for Asset Exchange between Permissioned Blockchains\\
\emph{World Wide Web journal, Special Issue on Emerging Blockchain Applications and Technology.}

\item[8.] \textbf{Martijn de Vos} and Johan Pouwelse, XChange: A Decentralized, Blockchain-based Mechanism for Generic Trade at Scale\\
Presented and discussed at the \emph{ninth Erasmus Liquidity Conference}, Rotterdam, The Netherlands, 2019 (no proceedings). Acceptance Rate \textbf{9.4\%} (11/117)

\item[\faFileTextO~~9.] \textbf{Martijn de Vos}, Mitchell Olsthoorn and Johan Pouwelse, DevID: Blockchain-based Portfolios for Software Developers\\
In \emph{Proceedings of the 1st IEEE International Conference on Decentralized Applications and Infrastructures (DAPPCON'19)}, San Fransisco, United States of America, 2019.

\item[\faFileTextO~~10.] \textbf{Martijn de Vos} and Johan Pouwelse, Real-time Money Routing by Trusting Strangers with your Funds\\
In \emph{Proceedings of the 17th International IFIP TC6 Networking Conference}, Zurich, Switzerland, 2018. Acceptance Rate 24\% (55/225)

\item[11.] Pim Otte, \textbf{Martijn de Vos} and Johan Pouwelse, TrustChain: A Sybil-resistant scalable blockchain\\
In \emph{Future Generation Computer Systems, Special Issue on Cryptocurrency and Blockchain Technology}, 2017, Elsevier.

\item[12.] Johan Pouwelse, André de Kok, Joost Fleuren, Peter Hoogendoorn, Raynor Vliegendhart, \textbf{Martijn de Vos}, Laws for creating trust in the blockchain age\\
In \emph{European Property Law Journal}, 2017, De Gruyter.

}\end{etaremune}

\vspace{0.5cm}
\noindent
\faFileTextO~~Included in this thesis.\\
%\faTrophy~~Won a best paper, tool demonstration, or proposal award.
